Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
words

Currently there is no known nuclear process that can explain the abundance variations in NGC 2419 without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.

@@

The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation. Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}. Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.

>>>>

Currently there is no known nuclear process that can explain the abundance variations in NGC 2419 without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude. Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could offer insight into the underestimation of K abundances in the Milky Way predicted by models \citep{kobayashi2011}. Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.

@@

The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
